Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-15 ms/manuscript.Rmd
Convert body text to one line per sentence
Fix fetching data used for model in MS
don't use sf_to_centroids()

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  # "plastome_calibration_dates",
  # FIXME: remove until phylo analysis is working "plastome_tree",
  "green_list",
  "model_params",
  "lrt_results",
  "aic_env_repro",
  "model_fits",
  "spatial_models"
))
```

@@

# Extract dataset used for model, including significance columns
biodiv_ferns_used_for_model <- sf_to_centroids(biodiv_ferns_spatial) %>%
  # filter to only sites used in model
  inner_join(
    spatial_models$model[[1]]$data %>% as_tibble() %>% select(grids),
    by = "grids"
  )

>>>>

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  # "plastome_calibration_dates",
  # FIXME: remove until phylo analysis is working "plastome_tree",
  "green_list",
  "model_params",
  "lrt_results",
  "aic_env_repro",
  "model_fits",
  "biodiv_ferns_cent"
))
```

@@

# Extract dataset used for model, including significance columns
biodiv_ferns_used_for_model <- biodiv_ferns_spatial %>%
  # drop geometry (only need centroids for modeling)
  st_set_geometry(NULL) %>%
  as_tibble() %>%
  # filter to only sites used in model
  inner_join(
    biodiv_ferns_cent %>% as_tibble() %>% select(grids),
    by = "grids"
  )
